Cosmological Evidences of Dark Matter through the CMB

### 2019-02-28 paper/main.tex
pdf produced

\section{Conclusion}
The Planck Collaboration estimated the density parameters with incredible precision:

>>>>

\section{Conclusion}
The discovery of the CMB marked the beginning of a new era of cosmology.
On one hand the challenge of precise measurements of the CMB anisotropies accelerated the technological progress.
On the other hand the theoretical effort to build a cosmological model of the universe consistent with the observations lead to the discovery of new form of matter and energy.
The combined results from the phenomenology of the primordial plasma with the measurements of the temperature anisotropies and other astronomical observations produced the following estimates of the density parameters:
\begin{equation*}
    \Omega_{b} = 0.04917 
\qquad \Omega_{\Lambda 0} = 0.6844 \qquad \Omega_{dm} = 0.2647 \qquad \Omega_{k0} = 0
\qquad \Omega_{r0} = 8.51 \times 10^{-5} 
\end{equation*}

The Planck Collaboration estimated the density parameters with incredible precision:
